Manuscript draft

### 2019-08-27 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

Many of our findings support and clarify previously published work; however we use a much larger and more comprehensive database than has previously been available, allowing for higher quality control and standardisation of data. This enalbed us to control for factors not previously controlled for - such as stand age, methodology, flux components, and disturbance regime - to gain a stronger understanding of latitudinal and climatic effects on productivity.

@@

This studies considers the relationship between productivity and climate on a coarse scale. Because of the nature of the ForC database, we were unable to access site-level MAT and MAP data for a number of sites, and lacked site-level data for other climate variables for all sites. As a result the climate data we used was primarily multi-year averages of annual climate measures from global databases. While the quality of these data is very high, we cannot expect that it captures detailed local variation in climate. Although we find that MAT is the strongest predictor for climate, part of this effect may be a result of the higher-quality stand-level dataset available for MAT. With high-quality stand-level data for other climate variables we might find stronger predictors. Similarly, with accurate stand-level measurements of growing season length, we would expect to record a stronger correlation between growing season length and productivity.

@@

Limitations: 
- We have only considered mature forests; there is a lot more work to go towards understanding the effect of stand age on productivity. In part, understanding these patterns will be reliant on acquiring more data at all stand ages.
- We have standardised data as far as possible; however there are still challenges with ensuring data quality is as high as possible. For example, there are inherent challenges with measuring stand-level productivity, particularly for certain components. Standardising BNPP in particular is challenging, as it is often sampled to insufficient depth/extrapolated from measures of ANPP. This means that, although we have been careful to control data selection within the database, we cannot entirely control the quality of data going into the database. As a result, our results are likely to be affected by this.
- As above, we are looking at climate data at a coarse scale; these are generalisations about large-scale patterns. Stand-level studies will help to improve our understanding of the effect of climate on productivity on smaller spatial and temporal scales.

>>>>

Many of our findings support and clarify previously published work; however we use a much larger and more comprehensive database than has previously been available, allowing for higher quality control and standardisation of data. This enabled us to control for factors not previously controlled for - such as stand age, methodology, flux components, and disturbance regime - to gain a stronger understanding of latitudinal and climatic effects on productivity.

@@

This studies considers the relationship between productivity and climate on a coarse scale. Because of the nature of the ForC database, we were unable to access site-level MAT and MAP data for a number of sites, and lacked site-level data for other climate variables for all sites. As a result the climate data we used was primarily multi-year averages of annual climate measures from global databases. While the quality of these data is high, we cannot expect that it captures detailed local variation in climate. Although we find that MAT is the strongest predictor for climate, part of this effect may be a result of the higher-quality stand-level dataset available for MAT. With high-quality stand-level data for other climate variables we might find stronger predictors. Similarly, with accurate stand-level measurements of growing season length, we would expect to record a stronger correlation between growing season length and productivity.

@@

Limitations: 
- We have only considered mature forests; there is a lot more work to go towards understanding the effect of stand age on productivity. In part, understanding these patterns will be reliant on acquiring more data at all stand ages.
